\documentclass[margin,line]{resume}
\newif\ifReferences
\newif\ifOnline
\usepackage{hyperref}

%Make bottom margin nicer
\addtolength{\textheight}{-0.75in}


\begin{document}

\Referencesfalse
\Onlinefalse


\name{\Large Connor Zanin}
\begin{resume}


\section{\mysidestyle Contact Information}
\ifOnline
	Email: zanin@ccs.neu.edu	 							\hfill Boston, MA\\
\else
    103 Norfolk Street \#7			                   			\hfill Cell: 781-879-2258\\
    Cambridge, MA 02139								        \hfill Email: zanin@ccs.neu.edu\\
    \mbox{}										\hfill Website: \url{ccs.neu.edu/home/zanin}\\
\fi
   




\section{\mysidestyle Research Interests}
Distributed Systems, Cloud Computing, Process Migration, Fault Tolerance and Recovery, Collaborative Systems


\section{\mysidestyle Education}
\textbf{Northeastern University}, Boston, MA \vspace{1mm}\\%
\textsl{PhD in Computer Science} \hfill \textbf{September 2016 -- present}\vspace{-3mm}\\\vspace{-1mm}%
\begin{list2}
	\item GPA: 3.7
	\item Expected Graduation: June 2021
	\item Advisors: Alan Mislove, Cristina Nita-Rotaru
\end{list2}

\textbf{University of Delaware}, Newark, DE \vspace{1mm}\\%
\textsl{B.S. in Computer Science} \hfill \textbf{September 2012 -- June 2016}\vspace{-3mm}\\\vspace{-1mm}%
\begin{list2}
	\item GPA: 3.7
    \item Graduated: May 2016
    \item Thesis: \textsl{Capturing the Mapreduce Performance Landscape}
    \item Advisor:  Dr. Michela Taufer
\end{list2}\vspace{-1.5mm}    



%\section{\mysidestyle Posters}


\section{\mysidestyle Professional Experience}
\textbf{Northeastern University}, Boston, MA\hfill\textbf{September 2016 -- present}\\
\textbf{Research Assistant}\hfill 
\vspace{-3mm}\\\vspace{-1mm}
\begin{list2}
	\item \filbreak\textit{PicoJump:} A system for process migration and load balancing. Enabling single-machine applications to execute correctly in a distributed environment and transparently to the operating system and application.
\end{list2}

\textbf{Global Computing Laboratory}, Newark, DE\hfill\textbf{May 2015 -- May 2016}\\
\textbf{Research Assistant}\hfill 
\vspace{-3mm}\\\vspace{-1mm}
\begin{list2}
	\item \filbreak\textit{HYPPO:} Developed a HYbrid Piece-wise POlynomial approach for optimizing MapReduce framework hyper-parameters.
\end{list2}

\textbf{EM Photonics}, Newark, DE\hfill\textbf{September 2014 -- May 2015}\\
\textbf{Software Engineering Intern}\hfill 
\vspace{-3mm}\\\vspace{-1mm}
\begin{list2}
	\item \filbreak\textit{Software development:} Developed features and fixed bugs for a video processing application.
\end{list2}

\textbf{Nasdaq OMX}, Marlborough, MA\hfill\textbf{June 2014 -- August 2014}\\
\textbf{QA Software Engineering Intern}\hfill 
\vspace{-3mm}\\\vspace{-1mm}
\begin{list2}
	\item \filbreak\textit{Performance testing automation:} Developed framework and tests for performance evaluation of a web application.
	\item \filbreak\textit{Performance evaluation:} Evaluated full-stack performance characteristics of a web application. Compiled findings in a reference document for business planning.
\end{list2}

\textbf{Lattice Engines}, Boston, MA\hfill\textbf{June 2013 -- August 2013}\\
\textbf{QA Software Engineering Intern}\hfill 
\vspace{-3mm}\\\vspace{-1mm}
\begin{list2}
	\item \filbreak\textit{Automated unit testing:} Developed automated testing for a web application. Made enhancements to the existing unit test framework.
\end{list2}

%\section{\mysidestyle Honors and Awards}
%Geoffery Eric Wright Outstanding Junior Award 2015
%\vspace{1mm}\\%
%Second place in Oregon for ACM Programming Competition 2015
%\vspace{1mm}\\%
%University of Oregon Dean's List (multiple terms)
%\vspace{1mm}\\%
%University of Oregon Presidential Scholarship 2013
%\vspace{1mm}\\%
%University of Oregon National Merit Scholarship 2013

\section{\mysidestyle Publications}

\filbreak
Connor Zanin, Katura Harvey, Liang Zhang, Deepak Garg, Thoephilus Benson, Dave Levin, and Alan Mislove.\\
``\textbf{PicoJump; A System for Transparently Migrating Processes to Resources}''
[Under Submission. 2018]

%\filbreak
%\section{\mysidestyle Relevant\\Skills} 
%\textbf{Programming Languages:} Python, C, C++, Java, C\#, ML\vspace{2mm}\\
%\textbf{Other:} OpenCV, SQL 


\filbreak
\vspace{-3mm}
\vspace{-2mm}
\section{\mysidestyle Relevant Courses}
Distributed Systems, Systems, Machine Learning,
Algorithms \& Data structures, Software Engineering,
Compilers, Virtualization

%\filbreak
%\section{\mysidestyle Activities}
%Organize group meetings for Networks and Distributed Systems Security PhD students\vspace{1.5mm}\\
%Endurance running\vspace{1.5mm}\\
%Organize and compete in tournaments for Super Smash Brothers\vspace{1.5mm}\\
 
%\filbreak
%\section{\mysidestyle Professional Affiliations}


%\filbreak
%\section{\mysidestyle References}
%\ifReferences
%	\begin{tabular}{@{}p{6cm}p{6cm}}
%	 \textbf{Dr. Cristina Nita-Rotaru} 	& \textbf{Dr. Sonia Fahmy}\\
%	 Associate Professor					& Professor\\
%	 Northeastern University				& Northeastern University\\
%	 Boston, MA			                	& Boston, MA \\
%	 phone: 765-496-6757					& phone: 765-494-6183\\
%	 email: crisn@cs.purdue.edu				& email: fahmy@cs.purdue.edu\\
%	 \end{tabular}
%
%\else % References
%	{\sl Available on request}
%\fi
\end{resume}
\end{document}
